Spatial considerations in the analysis of conservation data: evaluating the presence  of \textit{Acer campestre} (field maple) – space is special

### 2016-09-29 paper_v1.Rmd
Add files via upload

---
title: 'Spatial considerations in the analysis of conservation data: evaluating the presence  of \textit{Acer campestre} (field maple) – space is special'
author: "Alexis Comber^1^, Steve Carver^1^, Paul Harris^2^, Duccio Rocchini^3^"
output: pdf_document
geometry: margin=3cm
---

>>>>

---
title: 'Spatial considerations in the analysis of conservation data: evaluating the presence  of \textit{Acer campestre} (field maple) – space is special'
author: "Alexis Comber^1^, Steve Carver^1^, Paul Harris^2^, Carol Ximena Garzon-Lopez^3^, Duccio Rocchini^3^"
output: pdf_document
geometry: margin=3cm
---
